### 2018-01-08 1st_round_comments/1st_round_comments_final/comments.tex

1) Eq. 2.1, p.16: The second row is missing the charge, q, in front of Bz. This 
is not trivial, as the next 3 lines contain numerical examples that seem to be 
wrong. For instance, the range in $r_{0}$ quoted for DVCS is 20 - 45 mm - but I 
find a radius of 100 mm for 260 MeV/c 4He nuclei going radially (q = 2e). Even 
at some angle, 20 mm is impossible - such a track would never make it through 
the drift region. (Fig. 2.7 shows a minuscule pedestal below $r_{0}$ = 25 mm, but 
this must be due to some spurious effect - I don't see how you can reconstruct 
any tracks with $r_{0}$ < 30 mm). Is this mistake in your software as well (see 
horizontal scale in Fig. 2.7)?\\
\textcolor{blue}{
   In equation 2.1, the charge of the particle (q) is missed. Regarding the 
numerical calculations of $r_0$ for the elastic and the DVCS $^4$He, the 0.3 
factor is missed only in these calculations while the charge issue is taken 
into account. In the reconstruction software, both issues are properly 
implemented.  (For example, In a magnetic field of 4.5 T, the recoil 4He nuclei 
from DVCS (elastic) reaction have kinetic energies in the range [10, 25] ([17, 
35]) MeV, from momenta of [260, 450] ([360, 550]) MeV and $r_0$ [70, 150] 
([130,180]) mm.) }\\

2) Section 2.2: The RTPC calibration procedure is described in 2 steps: Event 
selection (2.2.1) and actual calibration (2.2.2 - 2.2.4) plus noise rejection 
(2.2.5). However, the event selection contains cuts on $r_0$, chi2, z etc.  
which in turn presuppose some initial calibration already. In other words, the 
process MUST be iterative - but I couldn't find a clear summary how this 
iteration was executed (i.e., what was used for the first iteration, how many 
iterations total, etc.). There is a short mention at the bottom of p. 27, but 
no details.\\
\textcolor{blue}{The drift paths and drift speed were first extracted using the 
MAGBOLTZ Monte Carlo simulation. One can find the detailed procedure of 
this first extraction in the BoNuS analysis note 
(https://www.jlab.org/Hall-B/secure/bonus/publication/BonusAnal110117.pdf).  
Then, we proceeded to derive empirical improvements with many iterations after 
each change that would affect the drift paths, such as the beam-offset
 and gain calibrations of the RTPC. Moreover after each pass, the number of
elastic events used for calibration increased. Overall, this was a long 
process that evolved and improved over the years and we concentrated in the 
note on the description of the final iteration.}\\

3) 2.2.1.1 It would be helpful to have some more background information: What 
is the longest drift time (from the inner radius) for a good track? What kind 
of momentum gives you only 4 hits, and are those events important? (see further 
down, under Fig. 3.19) What is the timing offset between the trigger and the 
shortest drift time (outer radius RTPC)? What is the average drift velocity and 
Lorentz angle? Conversion TDC-> time is given p. 15, but it would be much more 
helpful to have all these basic parameters collected in a single place: 2.1.1 - 
2.1.3 are all good places to summarize these parameters.\\
\textcolor{blue}{
  The longest drift time depend on $z$ but is typically around 6.6 $\mu$s. 
  Four is the number of the fired pads for each track, not the number of hits.  
  This value has been found to be reasonable from simulation, it mainly help 
  clean the sample and play very little role after other cuts. The time offset 
  is 15 TDCs (1 TDC= 114 ns), the average drift velocity is 6.14 $\mu$m/ns and 
  we did not extract the Lorentz angle, but MAGBOLTZ indicated about 20 
  degrees.}\\

4) 3rd bullet: There should also be an upper limit on $r_0$, since it is 
actually $r_0$ = +infinity that is indistinguishable from $r_0$ = -infinity 
(i.e., charge will be unknown). For the same reason, it would be nice to have a 
plot of $1/r_0$ instead of or in addition to Fig. 2.7 \\
\textcolor{blue}{Figure \ref{fig:1overr0} shows the 1/$r_0$
   distribution for a sample of the 1.2 GeV data for all the reconstructed 
   tracks without any requirement. Figure \ref{fig:good_r0} presents the same 
   distribution after requiring reading from at least 4 pads, $sdist$ and 
   $edist$ cuts. We see in figure \ref{fig:good_r0} that selecting 
   $r_0>0$ is already cutting the tail of the distribution. Applying a cut for 
   large $r_0$ would correspond to applying a cut at a larger $1/r_0$. Based on this
   distribution, we do not see any motivation for this. In particular since exclusivity
   cut will eventually clean all unphysical results.}\\
%  \textcolor{red}{Raph: Follow up on p49 bullet 4 of the note, you speak about 
   %  "the  mechanical supports between the two model of the RTPC". Beyond the 
   %  English, I remind you that there is not mechanical structure inside the 
   %  drift region in the eg6 RTPC. Please correct!} \\

@@

5) 4th bullet: How are the points $r^{helix}$, $\phi^{helix}$ and $z^{helix}$ 
determined?  Somehow, you have to identify points on a continuous line that are 
closest to (perhaps) the hits? How are the uncertainties (sigmas) in  
$\chi^{2}$ determined?  Are those the final values AFTER calibration? If so, 
how do you select your sample initially? (See above - it must be an iterative 
process).  \\
\textcolor{blue}{$(r^{helix},\phi^{helix},z^{helix})$ is the point
on the helix that is closest to the reconstructed hit position.
The values of the uncertainties are intrinsic detector properties depending
primarily on the size and configuration of the readout pads. These 
uncertainties, $(\sigma_{r}, \sigma_{\phi}, \sigma_{z}) = (0.53 mm, 2^{\circ}, 
1.2 mm)$, were not derived from our data and were held fixed.} \\

\textcolor{blue}{Equation 2.2 needs the beam-spot constraint added in
quadrature $\left(\frac{DOCA}{\sigma_r}\right)^2$ and the denominator adjusted
accordingly $(N_{pts}-5)$. It has to be written in full form as: (changed in 
the note as well).  }\\

\textcolor{blue}{
\begin{equation}
   \chi^{2} = \frac{\displaystyle \left(\frac{DOCA}{\sigma_r}\right)^2 
       + \sum_{i = 1}^{ N_{pts}} \left(\frac{r^{pt}_{i} 
      - r^{helix}_{i} }{\sigma_{r}}\right)^{2}  + \left( \frac{\phi^{pt}_{i} - 
      \phi^{helix}_{i} }{\sigma_{\phi}}\right)^{2} + \left( \frac{z^{pt}_{i} - 
      z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 5}
\end{equation}
}\\
%  \textcolor{green}{Raph: I did a minor change in the equation, to clarify 
%  that the beam spot term is not in the sum. To use in the note if you are 
%  ok.} \\

@@

11) Eq. 2.4: It is much better to use a cut on the reconstructed beam energy 
from the measured angles $\theta_e$ and $\theta_{He}$, since momenta are less 
precisely measured by CLAS than angles. Peter Bosted has used this method very 
effectively. Indeed, Fig. 2.13 shows a rather broad distribution, with a cut 
that barely has any effect. (This is a side comment, not meant to require 
additional work).\\
\textcolor{blue}{We are indeed aware of this, this is why we do use theta cut
as our main selection. Note also that $\delta\phi$ and $\delta z$ cuts have already
been applied in Figure 2.13's $\delta\theta$.}\\

12) Fig. 2.14: It's curious that the W distribution 'for the right RTPC module' 
is wider than on the lhs, given that nothing measured by the RTPC enters this 
quantity. However, it might be that the corresponding sectors in CLAS have 
different resolution, as well.\\
\textcolor{blue}{
Yes, this is related to the different resolutions of the corresponding CLAS sectors. 
This effect is large because, the reaction products are produced back to back 
results in small regions of overlapping acceptances of the RTPC and CLAS.  
In figure \ref{fig:W_sec}, we plot $W$ distributions corresponding to the 
different sectors in CLAS, one can immediately see the differences of resolution. }\\

@@

14) Figs. 2.20-22: Again, more detail needed to understand what's plotted and 
how it is calculated. Why is Delta-phi not zero for TDC = 15 (which corresponds 
to the outer radius of the drift region)?- Eq. 2.9: A (brief) derivation would 
help a lot here.\\
\textcolor{blue}{
$\Delta \phi$ at the anode (TDC = 15) is not equal to zero because there is a 
drift in phi between the anode (the first GEM layer at radial distance equal to 
60 mm) and the readout pads (at radial distance equal to 69mm). Regarding the 
derivation, figure \ref{fig:drift_derive} shows a simple drawing explaining how 
Eq. 2.9 has been derived.}\\
\textcolor{green}{Raph: Equations in the drawing need to be replaced by text.}

\begin{figure}[!h]
   \centering
   \includegraphics[height=12.5cm]{fig/drift_draw.png}
   \caption{Schematic drawing shows how the radius of emmision (R) at each 
   ionization point is calculated from the drift paths ($\Delta \phi$) and the 
drift speed ($DS$).}
   \label{fig:drift_derive}
\end{figure}

15) 2.2.4: Eq. 2.12 is differential, while Eq. 2.14 is integrated over the 
whole track. Do you integrate Eq. 2.12? Otherwise, it probably doesn't work all 
that well. Maybe this is the reason why the bands visible in Fig. 2.29 are not 
well represented by the superimposed curves? BTW, what is the vertical scale on 
Fig. 2.29?\\
\textcolor{blue}{Eq. 2.14 represents the average energy loss per unit of length in the 
track, $vtl$ being the visible track length. Assuming the energy loss in the 
drift region small, the two can be easily compared. Indeed at the lowest energy 
this assumption is not true anymore. But the difference between instantaneous 
and average $\frac{dE}{dx}$ is expected to be small compared to our 
resolution except very close to threshold (see right panel of Figure 
\ref{fig:energylosscorrection}).}
\textcolor{blue}{In Fig. 2.29 the bands are just there to guide the eye. Since the
vertical scale has never been carefully calibrated, we always present it in
arbitrary units. To have a feeling of the units, we have extracted an over all 
conversions from comparing real data to simulation, where 1 ADC is equal to 17 eV 
(21 eV) deposited in the left (right) module of the RTPC.} \\

16) p. 29, 2nd to last paragraph: I THINK I understand the Landau fit (over 
many tracks, no?) for each channel. But I don't understand the last step - why 
is it needed? What does it accomplish? For sure more details (and a plot) are 
needed.\\
\textcolor{blue}{
Yes, the gain ratio of each readout pad is calculated from comparing all the 
experimental elastic tracks to their corresponding tracks obtained from 
simulation. These ratios give us a first gain for each readout pad. However, 
we noticed that some pads record lower ADCs than expected (issue shown in 
figure 2.28) and noise. For these reasons, we wanted to make sure that the recorded 
ADCs by a given pad are similar to the recorded ADCs recorded by another pad in 
the same track. In figure~\ref{fig:dedxre}, one can see improvements obtained
by using this method to fine tune the gains obtained previously.} \\

\begin{figure}[!h]
\hspace{-0.5 cm}
\includegraphics[height=11.5cm]{fig/dedx_ratio_elastic.png}
\caption{The ratio between experimental dEdx and 
the simulated ones for different regions along $z$ of the RTPC. The blue lines 
are using the first method of extracting the gains (comparing the experimental 
recorded dEdx to the expected values calculated from the Bethe-Block formula), 
the violet lines are using the second method with a small fraction of our 
elastic events, the green lines are using the 1st pass of the second method 
(comparing simulation to data only) with all the elastic event sample and the 
brown lines are using the gains extracted from the second method (both steps).}
\label{fig:dedxre}
\end{figure}

@@

19) Fig. 2.30: What is plotted on the z-axis? (Occupancy?) Is this plot 
integrated over all 'good tracks', or only for tracks that actually traversed 
the selected pad (or a nearby pad)? If the former, what does a signal for a 
good track that crosses this pad look like?\\
  \textcolor{blue}{The color scale on the $z$-axis is a hit yield. The
hits included are only those recorded by one example noisy pad and only when
those hits were also included in a good track.} \\

@@

21) Fig. 2.37: Clearly, momenta are shifted 10$\%$ lower on average. This is 
not surprising, since at low momentum, energy loss will reduce the 
reconstructed radius of the helix. However, since the 4He momentum enters 
various cuts, we need a better understanding of Deltap/p as a function of p and 
theta, e.g. through 2D plots like Figs. 2.11-2.13. Of course it would be even 
better to CORRECT p for energy loss and other effects - but Section 3.3 doesn't 
mention any kinematic corrections for 4He. (I don't insist on this, but the 
effect on the 'true exclusivity' of the final cuts should be discussed.\\  
\textcolor{blue}{We do in fact correct for energy loss. The correction is 
calculated from energy loss in GEANT between the primary electron vertex and
the midpoint of the drift region. This correction was parameterized in terms 
of $(p,\theta)$ and particle type, it was validated by hand-integrating 
Bethe-Bloch formula. The left panel of Figure \ref{fig:energylosscorrection} 
shows our energy correction for a few polar angles. 
The following plots, \ref{fig:delta_p_p} and \ref{fig:delta_p_theta}, 
show that the momentum shift after the energy correction 
as a function of the measured momentum is still present. One could deduce
that our energy loss correction is not strong enough however 
no correlation is observed with the measured polar angle, which
should be expected if the mismatch was due to energy loss. Different
unidentified issues are probably at the origin of this problem.}\\
\textcolor{blue}{We decided to test corrections based on the z-dependence shown
in figure \ref{fig:delta_p_z}. Figure \ref{fig:P_diff_z_correction} shows the 
difference between the elastic 4He momentum the values from electron scattering 
angle. A second test was performed by doubling the energy loss, which gives 
correct momentum.  When applied on He4 DVCS, as shown in figure 
\ref{fig:dvcs_mom_corr}, we see a deterioration of the missing transverse 
momentum. We conclude that the momentum shift comes from more complicated 
effects linked to angles and possibly other experimental conditions and cannot 
be simply corrected
by a scale factor.}\\

@@

\begin{figure}[tbp]
\centering
\includegraphics[height=9.2cm]{fig/nphe_1_sectors.png}
\caption{Distribution of nphe emitted by electrons in the six sector of CLAS 
before the CLAS trigger change at run 61732.}
\label{fig:nphe_1}
\end{figure}

@@

25) p. 45 bottom: Are there any fiducial cuts to remove dead regions? Why 
not?\\
\textcolor{blue}{They are not implemented in this analysis as we deemed them
insignificant for this low statistics asymmetry measurement, particularly since
RTPC efficiency already shows a good agreement between LEFT/RIGHT in elastic scattering even
without removing dead regions (see answer to R1Q28 below and Figure~\ref{fig:tpceff}).}\\

26) Fig. 3.15: This may be my ignorance, but it looks like there is a 
secondary 'bump' between beta =0.9 and 1. What could it be? If it's neutrons, 
wouldn't that contribute to your background?\\
\textcolor{blue}{We seem to disagree there is a significant bump. However, if 
   there are some neutrons, they will be well removed by the following 
   exclusivity requirements. Also we want to point out the energy of the 
   neutral particle we use are greater than 2 GeV.  At such energies the time 
   of flight measurement from the EC is not good enough to separate neutrons 
   from photons anyway (see Fig.  \ref{fig:sim_coh} and 
\ref{fig:sim_incoh}).}\\

27) Bottom p.47: Indicate that the threshold on IC discris towards TDC has been 
too high to be useful and/or the flight path is too short to apply a beta cut 
as in EC.\\
\textcolor{blue}{
 The timing of the IC has is not functionning properly for certain channels. Therefore, 
 applying a timing cut would add inefficient regions in the detector that we 
 wanted to avoid. Moreover, the comment from previous answer applies as well,
such a cut would be very little help to reduce backgrounds at such high particle energies.}\\

28) Fig. 3.19:  The lhs of the RTPC apparently has only 1/2 the efficiency of the 
rhs. Is there any good explanation (at least qualitatively)? This could 
potentially distort phi-distributions, no? \\
\textcolor{blue}{This plot contains no good
   track cuts and so say very little about the efficiency. In more details, 
   This difference in the yield should not be linked to a different performance 
   of the RTPC.  They are due to the complicated convolution of CLAS and the 
   RTPC acceptance.  We measured the efficiency of RTPC using elastic 
scattering, and found that the left/right halves have similar efficiencies 
except near the upstream and downstream ends, as shown in 
Figure~\ref{fig:tpceff}.} \\

@@

\begin{figure}[tbp]
\centering
\includegraphics[height=6.2cm]{fig/npd_p_elastic.png}
\caption{The number of active pads versus the measured p/q for the good tracks 
collected using 1.2 GeV electron beam.}
\label{fig:padnb}
\end{figure}

@@

\textcolor{blue}{ Regarding the background, figure 
\ref{fig:delta_z_after_exclusitivty} shows $\Delta z$ distributions of the 
identified Coherent DVCS events after applying the exclusivity cuts without any 
initial constrain on $\Delta z$.}\\

\begin{figure}[tbp]
\centering
\includegraphics[height=6.2cm]{fig/rtpc_delta_z.png}
\caption{The z-vertex correspondence between the scattered electron and the 
recoil He4 for the identified coherent DVCS events after the exclusivity cuts 
in the two modules of the RTPC separately. Table \ref{table:Events_numbers} 
summarizes the cut numerically. }
\label{fig:delta_z_after_exclusitivty}
 \end{figure}

\begin{table}[!h]
   \centering
   \begin{center}
      \begin{tabular}{|l|l|l|}
         \hline
         \multicolumn{3}{ |c| }{Number of coherent DVCS events} \\
         \hline
         $\Delta z$ [mm] & Left module & Right module\\
         \hline
         [-50:-20] & 165 & 132 \\
         \hline
         [-20:20]  & 2736 & 2828\\
         \hline
         [20:50]   & 78 &  166 \\
         \hline
         Total     & 2979  & 3126 \\
         \hline 
      \end{tabular}
      \caption{The numbers of the identified coherent DVCS events in the 
      different regions in $\Delta z$ for the two modules of the RTPC.}
      \label{table:Events_numbers}
   \end{center}
\end{table}

>>>>

1) Eq. 2.1, p.16: The second row is missing the charge, q, in front of Bz. This 
is not trivial, as the next 3 lines contain numerical examples that seem to be 
wrong. For instance, the range in $r_{0}$ quoted for DVCS is 20 - 45 mm - but I 
find a radius of 100 mm for 260 MeV/c 4He nuclei going radially (q = 2e). Even 
at some angle, 20 mm is impossible - such a track would never make it through 
the drift region. (Fig. 2.7 shows a minuscule pedestal below $r_{0}$ = 25 mm, but 
this must be due to some spurious effect - I don't see how you can reconstruct 
any tracks with $r_{0}$ < 30 mm). Is this mistake in your software as well (see 
horizontal scale in Fig. 2.7)?\\
\textcolor{blue}{
   In equation 2.1, the charge of the particle (q) is indeed missing. Regarding the 
numerical calculations of $r_0$ for the elastic and the DVCS $^4$He, the 0.3 
factor is missing only in these calculations while the charge issue is taken 
into account. In the reconstruction software, both issues are properly 
implemented. (For example, In a magnetic field of 4.5 T, the recoil 4He nuclei 
from DVCS (elastic) reaction have kinetic energies in the range [10, 25] ([17, 
35]) MeV, from momenta of [260, 450] ([360, 550]) MeV and $r_0$ [70, 150] 
([130,180]) mm.) }\\

2) Section 2.2: The RTPC calibration procedure is described in 2 steps: Event 
selection (2.2.1) and actual calibration (2.2.2 - 2.2.4) plus noise rejection 
(2.2.5). However, the event selection contains cuts on $r_0$, chi2, z etc.  
which in turn presuppose some initial calibration already. In other words, the 
process MUST be iterative - but I couldn't find a clear summary how this 
iteration was executed (i.e., what was used for the first iteration, how many 
iterations total, etc.). There is a short mention at the bottom of p. 27, but 
no details.\\
\textcolor{blue}{The drift paths and drift speed were first extracted using the 
MAGBOLTZ Monte Carlo simulation. One can find the detailed procedure of 
a similar extraction in the BoNuS analysis note 
(https://www.jlab.org/Hall-B/secure/bonus/publication/BonusAnal110117.pdf).  
Then, we proceeded to derive empirical improvements with many iterations after 
each change that would affect the drift paths, such as the beam-offset
 and gain calibrations of the RTPC. Moreover after each pass, the number of
elastic events used for calibration increased. Overall, this was a long 
process that evolved and improved over the years and we concentrated in the 
note on the description of the final iteration.}\\

3) 2.2.1.1 It would be helpful to have some more background information: What 
is the longest drift time (from the inner radius) for a good track? What kind 
of momentum gives you only 4 hits, and are those events important? (see further 
down, under Fig. 3.19) What is the timing offset between the trigger and the 
shortest drift time (outer radius RTPC)? What is the average drift velocity and 
Lorentz angle? Conversion TDC-> time is given p. 15, but it would be much more 
helpful to have all these basic parameters collected in a single place: 2.1.1 - 
2.1.3 are all good places to summarize these parameters.\\
\textcolor{blue}{
  The longest drift time depend on $z$ but is typically around 6.6 $\mu$s. 
  Four is the number of the active pads for a track, not the number of hits.  
  This value has been found to be reasonable from simulation, it mainly help 
  clean the sample and plays very little role after other cuts. The time offset 
  is 15 TDCs (1 TDC= 114 ns), the average drift velocity is 6.14 $\mu$m/ns and 
  we did not extract the Lorentz angle, but MAGBOLTZ indicated about 20 
  degrees.}\\

4) 3rd bullet: There should also be an upper limit on $r_0$, since it is 
actually $r_0$ = +infinity that is indistinguishable from $r_0$ = -infinity 
(i.e., charge will be unknown). For the same reason, it would be nice to have a 
plot of $1/r_0$ instead of or in addition to Fig. 2.7 \\
\textcolor{blue}{Figure \ref{fig:1overr0} shows the 1/$r_0$
   distribution for a sample of the 1.2 GeV data for all the reconstructed 
   tracks without any requirement. Figure \ref{fig:good_r0} presents the same 
   distribution after requiring reading from at least 4 pads, $sdist$ and 
   $edist$ cuts. We see in figure \ref{fig:good_r0} that selecting 
   $r_0>0$ is already cutting the tail of the distribution. Applying a cut for 
   large $r_0$ would correspond to applying a cut at a larger $1/r_0$. Based on this
   distribution, we do not see any motivation for this. In particular since exclusivity
   cut will eventually clean all unphysical results.}\\

@@

5) 4th bullet: How are the points $r^{helix}$, $\phi^{helix}$ and $z^{helix}$ 
determined?  Somehow, you have to identify points on a continuous line that are 
closest to (perhaps) the hits? How are the uncertainties (sigmas) in  
$\chi^{2}$ determined?  Are those the final values AFTER calibration? If so, 
how do you select your sample initially? (See above - it must be an iterative 
process).  \\
\textcolor{blue}{$(r^{helix},\phi^{helix},z^{helix})$ is the point
on the helix that is closest to the reconstructed hit position.
The values of the uncertainties are intrinsic detector properties depending
primarily on the size and configuration of the readout pads. These 
uncertainties, $(\sigma_{r}, \sigma_{\phi}, \sigma_{z}) = (0.53 mm, 2^{\circ}, 
1.2 mm)$, were not derived from our data and were held fixed over all 
calibration itterations.} \\
\textcolor{blue}{Equation 2.2 needs the beam-spot constraint added in
quadrature $\left(\frac{DOCA}{\sigma_r}\right)^2$ as follows (changed in 
the note as well): }\\

\textcolor{blue}{
\begin{equation}
   \chi^{2} = \frac{\displaystyle \left(\frac{DOCA}{\sigma_r}\right)^2 
       + \sum_{i = 1}^{ N_{pts}} \left(\frac{r^{pt}_{i} 
      - r^{helix}_{i} }{\sigma_{r}}\right)^{2}  + \left( \frac{\phi^{pt}_{i} - 
      \phi^{helix}_{i} }{\sigma_{\phi}}\right)^{2} + \left( \frac{z^{pt}_{i} - 
   z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 4}
\end{equation}
}\\

@@

11) Eq. 2.4: It is much better to use a cut on the reconstructed beam energy 
from the measured angles $\theta_e$ and $\theta_{He}$, since momenta are less 
precisely measured by CLAS than angles. Peter Bosted has used this method very 
effectively. Indeed, Fig. 2.13 shows a rather broad distribution, with a cut 
that barely has any effect. (This is a side comment, not meant to require 
additional work).\\
\textcolor{blue}{We are indeed aware of this and we do use a $\Delta \theta$ cut
as our main selection for this reason, which we believe is equivalent to your
proposition. Note also that $\Delta\phi$ and 
$\Delta z$ cuts have already been applied in Figure 2.13's $\Delta\theta$.}\\

12) Fig. 2.14: It's curious that the W distribution 'for the right RTPC module' 
is wider than on the lhs, given that nothing measured by the RTPC enters this 
quantity. However, it might be that the corresponding sectors in CLAS have 
different resolution, as well.\\
\textcolor{blue}{
Yes, this is related to the different resolutions of the corresponding CLAS sectors. 
This effect is large because, the reaction products are emitted back to back 
resulting in small regions of overlapping acceptances of the RTPC and CLAS.  
In figure \ref{fig:W_sec}, we plot $W$ distributions corresponding to the 
different sectors in CLAS, one can immediately see the differences of resolution.}\\

@@

14) Figs. 2.20-22: Again, more detail needed to understand what's plotted and 
how it is calculated. Why is Delta-phi not zero for TDC = 15 (which corresponds 
to the outer radius of the drift region)?- Eq. 2.9: A (brief) derivation would 
help a lot here.\\
\textcolor{blue}{
$\Delta \phi$ at the anode (TDC = 15) is not equal to zero because there is a 
drift in $\phi$ between the anode (the first GEM layer at radial distance equal to 
60 mm) and the readout pads (at radial distance equal to 69mm). Regarding the 
derivation, figure \ref{fig:drift_derive} shows a simple drawing explaining how 
Eq. 2.9 can be derived.}\\

\begin{figure}[!h]
   \centering
   \includegraphics[height=6.5cm]{fig/deriv_R_drift.png}
   \caption{Schematic drawing shows how the radius of emmision (R) at each 
   ionization point is calculated from the drift paths ($\Delta \phi$) and the 
drift speed ($DS$).}
   \label{fig:drift_derive}
\end{figure}
\textcolor{blue}{In figure \ref{fig:drift_derive}, the radial distance of the 
   ionization point $k$, $R(TDC_{k})$, is equal to to the radial distance from 
   the target to the cathode, $R_{Min}$, plus the radial distances ($\sum 
   r_{i}$) that are caused by the drift from the first point of ionization at 
   $TDC_{max}$ to the point $k$. In each TDC bin, the radial drift distance 
($r_{i}$) is calculated as:}

   \begin{equation}
      r_{i} = \sqrt{DS^{2} - r_{i-1}  \bigg(\frac{\partial \Delta \phi} 
      {\partial TDC}(TDC_i) \bigg)^{2} }
\end{equation}
\textcolor{blue}{Adding all the terms, $R(TDC_{k})$ is formulated as:}
\begin{equation}
   R (TDC_{k}) = R_{min} + \sum\limits_{i=TDC_{Max}}^{TDC_{k}} r_{i}
\end{equation}

15) 2.2.4: Eq. 2.12 is differential, while Eq. 2.14 is integrated over the 
whole track. Do you integrate Eq. 2.12? Otherwise, it probably doesn't work all 
that well. Maybe this is the reason why the bands visible in Fig. 2.29 are not 
well represented by the superimposed curves? BTW, what is the vertical scale on 
Fig. 2.29?\\
\textcolor{blue}{Eq. 2.14 represents the average energy loss per unit of length in the 
track, $vtl$ being the visible track length. Assuming the energy loss in the 
drift region small, the two can be easily compared. Indeed at the lowest energy 
this assumption is not true anymore. But the difference between instantaneous 
and average $\frac{dE}{dx}$ is expected to be small compared to our 
resolution except very close to threshold (see right panel of Figure 
\ref{fig:energylosscorrection}).} \\
\textcolor{blue}{In Fig. 2.29 the lines are just there to guide the eye. Since the
vertical scale has never been carefully calibrated, we always present it in
arbitrary units. To have a feeling of the units, we have extracted an over all 
conversions from comparing real data to simulation, where 1 ADC is equal to 17 eV 
(21 eV) deposited in the left (right) module of the RTPC.} \\

16) p. 29, 2nd to last paragraph: I THINK I understand the Landau fit (over 
many tracks, no?) for each channel. But I don't understand the last step - why 
is it needed? What does it accomplish? For sure more details (and a plot) are 
needed.\\
\textcolor{blue}{
Yes, the gain ratio of each readout pad is calculated from comparing all the 
experimental elastic tracks to their corresponding tracks obtained from 
simulation. These ratios give us a first gain for each readout pad. However, 
we noticed that some pads record lower ADCs than expected (issue shown in 
figure 2.28) and sometime noise. For these reasons, we wanted to make sure that the recorded 
ADCs by a given pad are similar to the recorded ADCs recorded by another pad in 
the same track. In figure~\ref{fig:dedxre}, one can see improvements obtained
by using this method to fine tune the gains obtained previously.} \\

\begin{figure}[!h]
\hspace{-0.5 cm}
\includegraphics[height=11.5cm]{fig/dedx_ratio_elastic_NAB.png}
\caption{The ratio between the experimental dEdx and the simulated ones for 
   different regions along $z$ of the RTPC. The blue lines are using the first 
   method of extracting the gains (comparing the experimental recorded dEdx to 
   the expected values calculated from the Bethe-Block formula), the green 
lines are using the 1st pass of the second method (comparing simulation to data 
only) with all the elastic event sample and the brown lines are using the gains 
extracted from the second method (both steps).}
\label{fig:dedxre}
\end{figure}

@@

19) Fig. 2.30: What is plotted on the z-axis? (Occupancy?) Is this plot 
integrated over all 'good tracks', or only for tracks that actually traversed 
the selected pad (or a nearby pad)? If the former, what does a signal for a 
good track that crosses this pad look like?\\
  \textcolor{blue}{The color scale on the $z$-axis is a hit yield. The
hits included are only those recorded by one example noisy pad and only when
those hits were used in a good track.} \\

@@

21) Fig. 2.37: Clearly, momenta are shifted 10$\%$ lower on average. This is 
not surprising, since at low momentum, energy loss will reduce the 
reconstructed radius of the helix. However, since the 4He momentum enters 
various cuts, we need a better understanding of Deltap/p as a function of p and 
theta, e.g. through 2D plots like Figs. 2.11-2.13. Of course it would be even 
better to CORRECT p for energy loss and other effects - but Section 3.3 doesn't 
mention any kinematic corrections for 4He. (I don't insist on this, but the 
effect on the 'true exclusivity' of the final cuts should be discussed.\\  
\textcolor{blue}{We do in fact correct for energy loss. The correction is 
calculated from energy loss in GEANT between the primary electron vertex and
the midpoint of the drift region. This correction was parameterized in terms 
of $(p,\theta)$ and particle type, it was validated by hand-integrating 
Bethe-Bloch formula. The left panel of Figure \ref{fig:energylosscorrection} 
shows our energy correction for a few polar angles. 
The following plots, \ref{fig:delta_p_p} and \ref{fig:delta_p_theta}, 
show that the momentum shift after the energy correction 
as a function of the measured momentum is still present. One could deduce
that our energy loss correction is not strong enough however 
no correlation is observed with the measured polar angle, which
should be expected if the mismatch was due to energy loss. Different
unidentified issues are probably at the origin of this problem.}\\
\textcolor{blue}{We decided to test corrections based on the z-dependence shown
in figure \ref{fig:delta_p_z}. Figure \ref{fig:P_diff_z_correction} shows the 
difference between the elastic 4He momentum and its calculated value 
from the electron scattering 
angle. A second test was performed by doubling the energy loss, which gives 
correct momentum.  When applied on He4 DVCS, as shown in figure 
\ref{fig:dvcs_mom_corr}, we see a deterioration of the missing transverse 
momentum. We conclude that the momentum shift comes from more complicated 
effects linked to angles and possibly other experimental conditions and cannot 
be simply corrected
by a scale factor.}\\

@@

\begin{figure}[tbp]
\centering
\includegraphics[height=9.2cm]{fig/nphe_1_sectors.png}
\caption{Distribution of nphe emitted by electrons in the six sector of CLAS.}
\label{fig:nphe_1}
\end{figure}

@@

25) p. 45 bottom: Are there any fiducial cuts to remove dead regions? Why 
not?\\
\textcolor{blue}{They are not implemented in this analysis as we deemed them
insignificant for this low statistics asymmetry measurement.}\\

26) Fig. 3.15: This may be my ignorance, but it looks like there is a 
secondary 'bump' between beta =0.9 and 1. What could it be? If it's neutrons, 
wouldn't that contribute to your background?\\
\textcolor{blue}{We seem to disagree there is a significant bump. However, if 
   there are some neutrons, they will be highly suppressed by the DVCS
   exclusivity requirements. In particular we want to point out the energy of the 
   neutral particle is always greater than 2 GeV. At such energies the time 
   of flight measurement from the EC is not good enough to separate neutrons 
   from photons anyway (see Fig. \ref{fig:sim_coh} and \ref{fig:sim_incoh}).}\\

27) Bottom p.47: Indicate that the threshold on IC discris towards TDC has been 
too high to be useful and/or the flight path is too short to apply a beta cut 
as in EC.\\
\textcolor{blue}{
 The timing of the IC is not functionning properly for certain channels. Therefore, 
 applying a timing cut would add inefficient regions in the detector that we 
 wanted to avoid. Moreover, the comment from previous answer applies as well,
such a cut would be very little help to reduce backgrounds at such high particle energies.}\\

28) Fig. 3.19:  The lhs of the RTPC apparently has only 1/2 the efficiency of the 
rhs. Is there any good explanation (at least qualitatively)? This could 
potentially distort $phi$-distributions, no? \\
\textcolor{blue}{ 
   This difference in the yield should not be linked to a different performance 
   of the RTPC.  They are due to the complicated convolution of CLAS and the 
   RTPC acceptance.  We measured the efficiency of RTPC using elastic 
scattering, and found that the left/right halves have similar efficiencies 
except near the upstream and downstream ends, as shown in 
Figure~\ref{fig:tpceff}.} \\

@@

\begin{figure}[tbp]
\centering
\includegraphics[height=6.2cm]{fig/npd_p_elastic.png}
\caption{The number of active pads versus the measured p for the good tracks 
collected using 6 GeV electron beam.}
\label{fig:padnb}
\end{figure}

@@

\textcolor{blue}{ Regarding the background, figure 
\ref{fig:delta_z_after_exclusitivty} shows $\Delta z$ distributions of the 
identified Coherent DVCS events after applying the exclusivity cuts without any 
initial constrain on $\Delta z$.  This guides us to correct for these 
accidentals in our asymmetries in the form: $ A_{LU~~corr.} = \frac{1}{1 - 
contamination} A_{LU}$, with a 4.1$\%$ global accidental contamination.} \\

\begin{figure}[tbp]
\centering
\includegraphics[height=6.2cm]{fig/rtpc_delta_z.png}
\caption{The z-vertex correspondence between the scattered electron and the 
recoil He4 for the identified coherent DVCS events after the exclusivity cuts 
in the two modules of the RTPC separately without any initial constrains on 
z-vertices of the individual particles.  Table \ref{table:Events_numbers} 
summarizes the cut numerically.}

\label{fig:delta_z_after_exclusitivty}
 \end{figure}

\begin{table}[!h]
   \centering
   \begin{center}
      \begin{tabular}{|l|l|l|}
         \hline
         \multicolumn{3}{ |c| }{Number of coherent DVCS events} \\
         \hline
         $\Delta z$ [mm] & Left module & Right module\\
         \hline
         [-50:-30] & 42 & 77 \\
         \hline
         [-20:20]  & 2741 & 2856\\
         \hline
         [30:50]   & 34 &  78 \\
         \hline
         Contamination percentage  & 2.7$\%$  & 5.4$\%$ \\
         \hline 
      \end{tabular}
      \caption{The numbers of the identified coherent DVCS events in the 
      different regions in $\Delta z$ for the two modules of the RTPC.}
      \label{table:Events_numbers}
   \end{center}
\end{table}
